\documentclass{article}
\usepackage{setspace}
\usepackage{listings}
\usepackage{color}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{indentfirst}
\geometry{a4paper,bindingoffset=0.2in,%
	left=1in,right=1in,top=1in,bottom=1in,%
	footskip=.25in}

\onehalfspacing

%opening
\title{MECHTRON 4TB6: Contract \\ LifeLine}
\author{Group 30 \\ Emily Crowe, crowee \\ Arthur Faron, farona \\ Danushka Fernando, fernad12 \\Yerin Thevarajah, thevaryn \\ Phillip Truong, truonp1}

\begin{document}

    \date{November 18, 2021}
	\maketitle

	\newpage

	\section{Contract}
        LifeLine is a system that aims to provide four primary functions: quantitative measurements of primary vital signs, live sensor readout, data logging and data exporting. It is intended to be used as a portable device in first-aid situations to monitor vital signs and guide a first-aider to adapt and improve their treatment plan.\\
	
        We, Group 30, guarantee for our final demonstration to deliver the following
        \begin{itemize}
            \item The system will provide non-invasive monitoring of body temperature, blood pressure, and heart rate.     
            \item The system will help facilitate rapid assessment by providing feedback and visual aid through a GUI (graphical user interface) in order to speed up diagnosis and treatment of a casualty out in the field.
            \item The system will provide heart rate and body temperature measurements that are more frequent than existing manual methods while retaining sufficient accuracy for the user to perform a medical assessment of the casualty. 
            \item The system will monitor a person's blood pressure without a blood pressure cuff which is used in typical first aid situations.
            \item The system will give the user the option to save and record data collected during first aid so it can be exported to an external device. 
            \item The device will be portable enough to be carried in a backpack and held in one hand.  When operated as intended, the device will cause no harm such as electrical shock or injury to the casualty or user. \\ \\ \\
        \end{itemize} 
        
    Emily Crowe, crowee  \\ \\ \\

    Arthur Faron, farona \\ \\ \\
    
    Danushka Fernando, fernad12 \\ \\ \\

    Yerin Thevarajah, thevaryn \\ \\ \\
    
    Phillip Truong, truonp1
   
\end{document}